%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Professional experience}
  \begin{rSubsection}{Arizona State University (ASU)}{\em April 2019 -- Today}{Research apprenticeship on binary analysis}{Phoenix, United States of America}
    \item[]
      ASU's Security Engineering for Future Computing (SEFCOM) laboratory is a world-class cybersecurity research lab carrying out cutting-edge academic research.
    \item Design, implement, and evaluate a new, fast static binary analysis technique.
    \item Study state-of-the art: symbolic and concolic execution, fuzzing, automated exploit generation.
    \item Contribute to \href{https://angr.io/}{angr}, the open-source binary analysis framework.
    \item Guest lecturer for \href{https://www.tiffanybao.com/courses/cse545/}{CSE545 Software Security (Fall 2020)}: presentation, and live examples on using \href{https://angr.io/}{angr} to implement a static binary analysis technique.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{Mozilla Corporation}{\em May 2018 -- August 2018}{Web security intern, Scanning modern web applications with OWASP ZAP}{London, United Kingdom}
    \item[]
      The Firefox Operations Security team protects the core services and release engineering infrastructures Mozilla relies on to build, ship and run Firefox.
    \item[]
      OWASP ZAP is a free and open-sourced security tools to help automatically find security vulnerabilities in web applications.

    \item Research and development in Javascript and the DOM API: keep track of events and interactions happening in a webpage. Released the \href{https://www.npmjs.com/package/@zaproxy/front-end-tracker}{@zaproxy/front-end-tracker} library on npm.
    \item Development of a ZAP add-on to create a framework for pentesters to run security scripts directly in the browser.
    \item Research on modern web applications (Single Page Applications) vulnerabilities.
    \item Part of a distributed team and contributing to an open-source community.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{Orange Application for Business}{\em June 2017 -- August 2017}{System administrator, Securing workstations}{Bordeaux, France}
    \item[]
      OAB is a subsidiary of Orange S.A developing and hosting services for businesses.
    \item[]
      Integrated to an operations team of four, my mission was to secure their Linux workstations.

    \item System administration: Arch, Ubuntu, Debian.
    \item Define and apply good security practices for laptops and mobile devices.
    \item Development: ansible roles, \href{https://github.com/multimediabs/audit-ssh-client-config}{audit-ssh-client-config} script.
    \item Research: securing the boot process (anti-evil maid), NixOS, Public Key Infrastructures.
    \item Training and communication about the security practices: write documentation, create tutorials, run workshops.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{RedShield Security Ltd}{\em January 2015 -- April 2016}{Software engineer}{Wellington, New Zealand}
    \item[]
      Shielding-with-a-service company providing a web application firewall, vulnerability scanner and analyzer to assist IT departments ensure the security of their systems.

    \item Development in Ruby and Javascript; Debugging, and automate testing.
    \item Configuration of production and CI servers (Jenkins).
    \item Security: offensive, secure development, incident response.
  \end{rSubsection}

  %------------------------------------------------

  \begin{rSubsection}{CER SNCF}{\em June 2012 -- Oct 2014}{Full-stack developer}{Bordeaux, France}
    \item[] Distributed all over the Aquitaine and Poitou Charentes French regions, the CER (for Committee of Regionnal Establishment) provides services to SNCF's workers.

    \textbf{Missions}
      \item Web development, information system administration and maintenance, automation.
      \item IT service management: needs analysis; goals, processes, and tasks definition; listing of skills and resources to prioritize our work.
      \item Help in recruitment for IT service: define required skills, and mission scopes; Interview candidates.

    \textbf{Project, subject of my master thesis}
      \item Build a website dedicated to SNCF's employees: tasks and planning definition, resources and skills affectation to provide this new service within six months with a three person team.
      \item Communication and product launching: define and reach targets, follow the adoption and usage of the product.
      \item Integration within the existing information system: shared databases services, web server deployment.
      \item Server on Ubuntu 14.04, database is PostgreSQL, Nginx and Unicorn as web stack.
      \item Application built with Ruby-On-Rails, Slim, SASS and CoffeeScript. RSpec and Capybara for testing and QA.

  \end{rSubsection}

\end{rSection}
