%----------------------------------------------------------------------------------------
% PROJECTS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Projects and competitions}

  \begin{rSubsection}{LibraryBox}{\em December 2014 -- Today}{web development, association}{}
    \item[] Development of a clear an good looking web interface for LibraryBoxes.
    \item Web development, front-end using AngularJS, Bower for libraries management and Gulp as build system.
    \item Available on Github: \href{https://github.com/Labx/LibraryBox-app}{github.com/Labx/LibraryBox-app} .
  \end{rSubsection}

  \begin{rSubsection}{CarrotMob France}{\em June 2014 -- September 2014}{web development, positive change}{}
    \item[] Carrotmob France is a French non profit association organizing buycotts events to reward business's commitment to making socially responsible changes to the business.
    \item Causes: social, economic and environmental positives changes.
    \item About ten persons organized for remote work and Scrum method using Trello, Hangout, Skype and \href{https://github.com/carrotcommunity/carrotmobfrance}{Github}.
    \item Web development, front and back-end using SailsJS, Bower, Jade and Grunt tasks.
  \end{rSubsection}

  \begin{rSubsection}{Personal dedicated server}{\em 2014 -- Today}{server administration}{}
    \item[] Co-owner of a dedicated server, used to manage personal services such as Owncloud, Selfoss, Etherpad, Wallabag and websites.
    \item Configuration: Nginx reverse proxy for several web-servers.
    \item Server securisation: users authentication, services rights and responsibility.
    \item Private Git repositories management.
  \end{rSubsection}

  \begin{rSubsection}{Hackaton OpenData}{\em 2013}{web development, management, entrepreneurship}{}
    \item[] In response to the call for proposals done by Gironde communities (AEC, CUB and CG33), some volunteers regrouped to establish a web service which Gironde's citizens could use to search and find places to throw their waste.
    \item Self organized seven persons team.
    \item Application developed with AngularJS and served by Ruby.
    \item Proof of concept available at: \href{http://wheredrop.eu01.aws.af.cm/#/}{http://wheredrop.eu01.aws.af.cm/\#/} .
  \end{rSubsection}

  \begin{rSubsection}{StartUp WeekEnd}{\em March 2013}{entrepreneurship, communication}{Toulouse, Midi-Pyr\'{e}n\'{e}es}
    \item[] Project idea to create an ultra-portable home console. Market analysis, identification of customers, product design, marketing, fundraising, etc. Presentation of the project in front of a jury and public.
  \end{rSubsection}

  \begin{rSubsection}{Imagine Cup}{\em 2011 and 2013}{games development, management}{}
    \item[] Participation at the Imagine Cup competition organized by Microsoft. With a four students team, we developed video games with Silverlight and XNA around the themes of hunger in the world and the overproduction of waste in about four to five months. World Top 13 with Team Rocket team in 2011.
  \end{rSubsection}

  \begin{rSubsection}{BeMyApp event}{\em November 2012}{mobile development, team management, entrepreneurship}{Marseille, Provence-Alpes-C\^{o}te d'Azur}
    \item[] First prize awarded in Gironde about a competition of mobile application development in 48 hours with the following constraint: use open data to highlight tourism of our country. Organizing a team of six people, development and finally presentation of the project in front of a jury and public.
  \end{rSubsection}

\end{rSection}
