%----------------------------------------------------------------------------------------
% SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}

  \begin{rSubsection}{Software development}{}{}{}

    \emph{Languages}
    \vspace{-7pt}
    \begin{center}
        \begin{tabular}
            {c | c | c | c | c | c | c}
            Ruby & Javascript & PHP & Latex & C\# & Python & Java \\
            \score{4}{5} & \score{4}{5} & \score{3}{5} & \score{4}{5} & \score{3}{5} & \score{3}{5} & \score{3}{5}
            \vspace{5pt}
        \end{tabular}
        \begin{tabular}
            {c | c | c | c}
            Bash & C & ASM x86 & Scheme\\
            \score{3}{5} & \score{3}{5} & \score{1}{5} & \score{2}{5}
        \end{tabular}
    \end{center}

    \emph{Libraries / frameworks}
    \vspace{-7pt}
    \begin{center}
        \begin{tabular}
            {c | c | c | c | c | c | c | c | c}
            Ruby-On-Rails & ExpressJS & Angular & SailsJS & Pygame & XNA & Zend & jQuery & CodeIgniter \\
        \end{tabular}
    \end{center}

  \end{rSubsection}


  \begin{rSubsection}{Systems administration}{}{}{}
    \item Ubuntu, Linux Mint and Windows8 user.
    \item Accustomed to use and manage Debian based systems: Raspbian, Ubuntu desktop and server, Debian.
    \item Nginx reverse proxy and / or load-balancer, Unicorn, Apache2 and Express (Node.js) web-servers.
    \item Oracle and SQLServer at school ; MySQL, PostgreSQL, Redis and MongoDB experienced and used in projects.
    \item Source code version control system: some SVN and much Git.
    \item Continuous integration: Jenkins, Docker, Capistrano, Ansible and Chef.
  \end{rSubsection}


  \begin{rSubsection}{Soft skills}{}{}{}
    \item Team management: implement the environment which allows to develop the products and achieve goals.
    \item Used to Agile methods, especially Scrum. Pair programming and TDD practice.
    \item Speaker: animation and presentation about a product, a project or to share experiences.
    \item Interpersonal: listening and understanding individuals to facilitate interactions within a group.
    \item Marketing: around and through a product and / or company to communicate values.
  \end{rSubsection}

\end{rSection}
